---
title: "Hello, Penguins"
format: 
  revealjs: default
editor: visual
execute:
  echo: true
 

# title: "quarto-revealjs"
# format: html
# editor: visual
# execute: 
#   echo: false
bibliography: references.bib
---
# Introduction 

## Using Quarto *revealjs* slide-deck  

-   [See 11:00](https://www.youtube.com/watch?v=_f3latmOhew&t=980s) to modify format for PDF, html and *revealjs* slide decks.

-   [See 13:00](https://www.youtube.com/watch?v=_f3latmOhew&t=980s) to see use of *predefined classes* in the Visual editor, like css to modify *attributes*.  You might, for example, wish to make text a bit smaller.  

-  [See 14:00](https://www.youtube.com/watch?v=_f3latmOhew&t=980s) to modify *execute: echo: true* to show code.  

- Modify *Species* code chunk to:  
  - #| output-location: column-fragment  
  - #| output-location: slide


## Data

Using the `penguins` dataset from [palmerpenguins](https://allisonhorst.github.io/palmerpenguins/articles/intro.html) package. [@gorman2014]

```{r}
#| label:  load-package
#| message: false

library(tidyverse)
library(ggthemes)
library(palmerpenguins)
library(gt)

data("penguins")

```

```{r}
glimpse(penguins)
```

## Species

The figure below is a scatter plot of species of penguins.

<u>To add *cross-reference*</u>\
1. Use word *fig* at the beginning of the label.\
- *fig-bill-dims-species*

2.  **For a caption**, use #\| fig-cap: A scatterplot of ....\

-   *Do not* use a pipe after "fig-cap:"

## Species code chunk

```{r}
#| eval: false
#| label: fig-bill-dims-species
#| fig-width: 5
#| fig-asp: 0.618
#  Add alternative text for the figure. This fig-alt text will show up in "inspect" function.  
#| fig-alt: |
#| A scatterplot of penguins' bill depth and length, colored by 
#| species of penguins.  There is a relatively strong, linear association.
#| fig-cap: |
#|  A scatterplot of penguins' bill depth and length, colored by species of penguins. 
#| output-location: columnn-fragment 

ggplot(
  penguins,
  aes(
    x = bill_length_mm, y = bill_depth_mm,
    color = species, shape = species
  )
) +
  geom_point() +
  theme_minimal() +
  scale_color_colorblind() +
  labs(x = "Bill length (mm)", y = "Bill depth (mm)")
```

## Captioning and cross-referencing in Quarto

```{r}
#| label: fig-claudes_figure
#| warning: false
#| fig-width: 5
#| fig-asp: 0.618
#| fig-alt: "A scatterplot of penguins bill depth and length, colored by species of penguins. There is a relatively strong, linear association."
#| fig-cap: "A scatterplot of penguins bill depth and length, colored by species of penguins."

ggplot(
  penguins,
  aes(
    x = bill_length_mm, y = bill_depth_mm,
    color = species, shape = species
  )
) +
  geom_point() +
  theme_minimal() +
  scale_color_colorblind() +
  labs(x = "Bill length (mm)", y = "Bill depth (mm)")
```

## Cross-referencing 
Make sure that the **cross-referencing** is set up correctly. To cross-reference the figure, you can use the `@fig-label syntax` in your Quarto document. For example, you can reference the figure like this:

As shown in @fig-claudes_figure, there is a clear relationship between bill depth and length among different species of penguins.

## **To summarize**:

* Use the `#| fig-cap: "Your caption text"` syntax in the code chunk options to set the figure caption. - Use the `#| fig-alt: "Your alternative text"` syntax to provide alternative text for accessibility purposes. 
* Use the `@fig-label` syntax in your Quarto document to cross-reference the figure, replacing `label` with the actual label you assigned to the figure code chunk.

* These features in Quarto allow you to create well-documented and accessible documents that are easy to navigate and reference.

If you have any more questions or need further assistance with Quarto, feel free to ask. I'm here to help you learn and make the most out of Quarto's features!

## Penguins

@tbl-penguins-top10 shows the first 10 penguins from the dataset.

```{r}
#| label: tbl-penguins-top10
#| tbl-cap: "First 10 penguins"

penguins |>
  slice_head(n = 10) |>
  select(species, bill_length_mm, bill_depth_mm) |>
  gt()
```


# Analysis 

# References  
